---
title: 'Data Visualization in R using ggplot2'
author: '<div style = "text-align: left;"><font size="7">By <br> Avinash Prabhakaran</font></div>'
date: "19/11/2017"
output: 
  ioslides_presentation:
    widescreen: true
    smaller: true
    incremental: true

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(fig.align = "center")
```

```{r}
library(tidyverse)
library(forcats)
library(gridExtra)
library(knitr)

library(tm)
library(SnowballC)
library(wordcloud)
library(RColorBrewer)

library(gapminder)
library(gganimate)
library(ggrepel)
library(ggthemes)
```
<style>
h2 {
text-align: center;
font-size: 150%;
}

.middle {
text-align: center;
}
</style>


## Why ggplot2?

### 1. Breaks graphs into semantics and components such as scales and layers

### 2. Professional quality graphs

### 3. Literate programming

### 4. Modularity

### 5. Easy superposition (Multiple Plots in a graph)

### 3. Multiple color schemes + RColorBrewer

### 6. Multiple themes + ggthemes

### 5. Large number of extention libraries

### More reasons why you should use ggplo2: https://github.com/tidyverse/ggplot2/wiki/Why-use-ggplot2